Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-17 paper/paper.tex
changes to pill section of paper Tested everything on crystal.

We test cells of radius $.5\micron$ and of lengths $2\micron$,
$3\micron$, $4\micron$, and $5\micron$ measured from the tip of one
end cap to the tip of the other \fixme{I'm running the 2,3,5 pills
  again to make sure that everything in this paragraph is true}. In
each case, we observe in the deterministic simulations a quick
establishement (within a few periods) of extremely regular oscillatory
behavoir that lasts indefinitely.  The stochastic results show
oscillitions that are similarly regular in time, with periods that
nearly match those of the deterministic (they differ roughly by a
factor of .05) \fixme{does this square with the correlation data
  periods?}. The regularity of the pill shape cell periods is
discussed below, in our analysis of time correlation data \fixme{not
  written yet}.  These periods increase with cell length, as shown in
Table~\ref{tab:pill-periods}, in agreement with the results of Huang
\emph{et al.}.

@@

While the stochastic results show periods that seem to have a high
degree of regularity as well as similarity to the deterministic
results, they do differ in the precise locations of the maxima.  While
the deterministic simulations show maxima that are every time
concentrated in the center of one of the cell ends, with a symmetric
smear of protein going out laterally to either side, the stochastic
simulations show maxima that, while always located somehwere in the
end region of the cell, occur at different positions within this
region.  This is reflected in Figure~\ref{image-p}, which shows
periods that are the same and qualitative behavoir that is
approximately the same, but also that there is variation in the
details of the stochastic simulation maxima location.

@@

\fixme{Originally the 'Stability Analysis' section came next.  I would
  like to still mention the results of this, since Huang only did the
  analysis on the cylinders, and we've done it on the flattened shapes
  and shown that it works with those too.  But I don't know where to
  fit in the paragraph or so that it would take.  For now I've just
  put the whole section at the end of the paper.}

>>>>

We test cells of radius $.5\micron$ and of lengths $2\micron$,
$3\micron$, $4\micron$, and $5\micron$ measured from the tip of one
end cap to the tip of the other \fixme{I'm running the 2,3,5 pills
  again to make sure that everything in this paragraph is true}. In
each case, we observe in the deterministic simulations a quick
establishement (within a few periods) of regular oscillatory behavoir
that lasts indefinitely.  This temporal regularity can be seen in
Figure~\ref{corr-pill}, which shows the temporal correlation of the
total MinD protein located in the the two polar sections of the cell.
In the stochastic simulations the pills exhibit coherence times of
over 7 periods and the determinisitic version cohere indefinately.

@@

While the stochastic results show periods that seem to have a high
degree of regularity as well as similarity to the deterministic
results, they do differ in the precise locations of the maxima.  While
the deterministic simulations show maxima that are every time
concentrated in the center of one of the cell ends, with a symmetric
smear of protein going out laterally to either side, the stochastic
simulations show maxima that, while always located somehwere in the
polar region of the cell, occur at different positions within this
region.  This is reflected in Figure~\ref{image-p}, which shows
periods that are the same and qualitative behavoir that is
approximately the same, but also that there is variation in the
details of the stochastic simulation maxima location.

\fixme{Is the table of the cell periods needed? I'm not sure if we
  have a experiment to compare this to} The stochastic results show
oscillitions that are similarly regular in time, with periods that
nearly match those of the deterministic (they differ roughly by a
factor of .05) \fixme{does this square with the correlation data
  periods?}. The regularity of the pill shape cell periods is
discussed below, in our analysis of time correlation data \fixme{not
  written yet}.  These periods increase with cell length, as shown in
Table~\ref{tab:pill-periods}, in agreement with the results of Huang
\emph{et al.}.

@@
